---
title: "Final Project of Practical Machine Learning Course"
author: "Rodolfo Deusdara"
date: "15/11/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Background

Using devices such as Jawbone Up, Nike FuelBand, and Fitbit it is now possible to collect a large amount of data about personal activity relatively inexpensively. These type of devices are part of the quantified self movement – a group of enthusiasts who take measurements about themselves regularly to improve their health, to find patterns in their behavior, or because they are tech geeks. One thing that people regularly do is quantify how much of a particular activity they do, but they rarely quantify how well they do it. In this project, your goal will be to use data from accelerometers on the belt, forearm, arm, and dumbell of 6 participants. They were asked to perform barbell lifts correctly and incorrectly in 5 different ways. More information is available from the website here: http://web.archive.org/web/20161224072740/http:/groupware.les.inf.puc-rio.br/har (see the section on the Weight Lifting Exercise Dataset).

```{r}
# Creating training and testing obejcts
training <- read.csv("pml-training.csv", na.strings=c("NA","#DIV/0!", ""))  
testing <- read.csv("pml-testing.csv",  na.strings=c("NA","#DIV/0!", ""))
# Checking dimensions
dim(training)
dim(testing)
# Cleaning missing data
training <- training[,colSums(is.na(training))==0]
testing <- testing[,colSums(is.na(testing))==0]
# Checking dimensions
dim(training)
dim(testing)
# We are not going to use the seven first columns in our analysis
training<-training[,-c(1:7)]
testing<-testing[,-c(1:7)]
dim(training)
dim(testing)
#Seeting seed
set.seed(12345)
# Creating Data Partition
library(caret)
intrain <- createDataPartition(training$classe, p=0.75, list=FALSE)
training1 <- training[intrain,]
testing1 <- training[-intrain,]
dim(training1)
#Training and predicting with Classification Tree
fitControl <- trainControl(method = "cv", number = 5, allowParallel = TRUE)

fit_CT <- train(classe ~., data = training1, method = "rpart", trControl = fitControl)
pred_CT <- predict(fit_CT, newdata = testing1)
# Accuracy
confusionMatrix(pred_CT, testing1$classe)

# Training and predicting with Gradient Boosting Machine
fit_GBM <- train(classe ~., data = training1, method="gbm", trControl = fitControl)
pred_GBM <- predict(fit_GBM, newdata=testing1)
#Accuracy
confusionMatrix(pred_GBM, testing1$classe)

# Training and predicting with Random Forest
fit_RF <- train(classe ~ ., data=training1, method = "rf", trControl = fitControl)
pred_RF <- predict(fit_RF, newdata=testing1)
#Accuracy
confusionMatrix(pred_RF, testing1$classe)

# Conclusion- Random forest is the best
# Final prediction
Finalprediction <- predict(fit_RF, newdata=testing)
Finalprediction
```


